On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-06 Manuscript/reply.tex
Removed quoted text

\jy{For each comment, response first and at the end of each response,
  state what was done in the text. I usually don't quote text because
  if you make changes, you need to synchronize at two locations. Learn
  from the first version (which is a real reply letter for a paper).}

@@

We have added this comment to the Recentered Percentile CI paragraph:
The motivation behind proposing such an interval was based on the 
simulation performance of the BC and BCA intervals, which will be discussed
further in the Results section.

After discussion of the flaws of percentile, BC, and BCA CIs at the end of the
first paragraph of Discussion, we have included these additional comments on
why the proposed CI performs well:

The uncertainty measure from bootstrap, which is used to determine the width of
the percentile CI, is quite consistent in comparison to that used for BC and 
BCA CIs. However, for a percentile CI, the center seems
to be at the wrong location but is corrected when $\hat\theta_n$ is used as the
center. This is most likely the reason why the proposed recentered percentile CI
perfoms so much better than percentile, BC, and BCA CIs.

@@

\jy{never use ``below'' because tables/figures are floats.}

Figure~\ref{fig:mu} is an example of what this would look like. We find that it 
is a little
cluttered to make comparisons, so we will use the original format.

\jy{1. Reduce the heights; put legend at the bottom; put the
  confidence intervals side by side for each sample size (see this
  paper for example plot:
  \url{https://iopscience.iop.org/article/10.1088/1748-9326/ac14ee/meta}.}
\mc{addressed}

@@

@@

The text from the Appendix has been moved to the Simulation Study 
section. The second reviewer suggested block size as an additional experimental
factor, so the paragraphs for normal and exponential error structures have
been adjusted accordingly.

@@

We have included this comment in the Exponential Marginal Distribution 
subsection of the Design section:

It is important to note that we expect the CIs that are based on bootstrap 
``tables" to depend on the 
asymptotic distribution of the statistics, but we expect such CIs to 
have similar performance for different error structures. For example, under the 
Central
Limit Theorem, we expect the asymptotic distribution of the sample mean to be 
approximately 
normal for both marginal normal distributions and marginal exponential 
distributions. Therefore, we do not expect CIs that are not based on bootstrap
``tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better under
non-normal error structures.
\eds{you will need to add more here.  This concerns the
(asymptotic) distribution of the statistics, not the underlying error 
structure.}
\mc{I changed it a bit... I'm not sure what to say for circumstances in which
“non-parametric” CI 
formulas would work better}

@@

We agree. We have added this comment to the discussion:

Lastly, because of its exceptional performance in comparison to the other 
CIs that are not based on bootstrap ``tables", the proposed recentered percentile 
CI would be
an interesting method to study further with different bootstrap schemes.

@@

Thank you for pointing this out. We modified the Design section to include a 
specification of the interval type for the coverage rate:

Because it is unlikely for the coverage to 
exactly match the nominal level, we can construct a 95\% Wald-type CI of the 
coverage rate 
(which is an estimate of a proportion with $R = 10000$). If the proportion 0.95 
is included in the interval, the block bootstrap method is likely performing 
well. If all values in the interval are below 0.95, the results would suggest 
that the method either is providing inaccurate estimation, is underestimating 
the process' variability, or a combination of both. If all values in the 
interval are above .95, the results suggest that the method is overestimating 
the process' variability. \citet{brown2001interval} notes that the Wald-type 
interval has poor coverage as the proportion approaches 0 or 1.

@@

We have also included these comments and a figure in the Results section which 
uses exact 
Clopper-Pearson CIs:

@@

Because of the deterioration for $\phi$, we found it hard to fix the limits on 
the 
y-axis without hurting the visualization for the other rows. 
Figure~\ref{fig:alt_phi1} is an 
example:  \eds{refer to the Figure label, and avoid using `below' and `above'
terminology with latex because the figures are not always positioned as we may
have intended.}
\mc{addressed}

@@

We have included this comment at the end of the paragraph on estimation of 
$\mu$:

A possible explanation for this is that if a 
stationary series has a positive 
autocorrelation, the effective sample
size is decreased, whereas is a series has a negative autocorrelation, the
effective sample size is increased. Additionally, this seems to have a 
greater effect on the the estimation of the location parameter versus that
of the scale parameter or temporal dependence parameter.

@@

Thank you for pointing this out. The original sentence has been replaced 
with:

Coverage rates are acceptable at smaller sample 
sizes when phi is positive versus when phi is negative. In
other words, a larger sample size is generally required to estimate a 
parameter for a sample with a negative $\phi$ versus a positive $\phi$ of the 
same magnitude.

@@

\citep{calhoun2018}

@@

We have now repeated the same simulation study with block size as an 
additional experimental factor. The optimal order of block size is 
$\lceil n^{1/3} \rceil$, so we tried the same simulations using 
$l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$. We have included
an Appendix detailing these results:

\eds{\@ Jun: what do you think about putting the $l = \lceil 2n^{1/3} \rceil$
results in the Appendix, but keeping the conclusions regarding how the 
$l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$ simulations differ
in the main text?} \jy{I agree. Mention the results in the text and
refer to the appendix.}
\mc{I moved everything to the Appendix. if you want to change it back you can 
revert the commit}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_norm_mu_1}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
    normal distribution with AR coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
    error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:mu1}
\end{figure}

\begin{figure}[bp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_norm_sigma_1}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal standard deviation $\sigma_x$ of an AR(1) process with a
    marginal standard normal distribution with AR 
    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
    block bootstrap with $l = \lceil n^{1/3} \rceil$. The 
    error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:sigma1}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_norm_phi_1}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
    a marginal standard normal distribution with 
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
    error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:phi1}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_mu_1}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal mean $\mu$ of a stationary series with marginal unit exponential
    distribution obtained by transforming an AR(1) process with
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_mu1}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_sigma_1}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
    of a stationary series with 
    marginal unit exponential distribution obtained by transforming an AR(1) process
    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
    replicates of
    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_sigma1}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_phi_1}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
    the first-order autocorrelation coefficient of a stationary series
    with marginal unit exponential distribution obtained by transforming an AR(1) 
    process with 
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
    replicates of
    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_phi1}
\end{figure}

\section*{Appendix: Simulation Study with $l = \lceil 2n^{1/3} \rceil$}

\textbf{Figures~\ref{fig:mu2}--\ref{fig:phi2}} 
summarizes the empirical coverage rates and the 95\% confidence intervals of the 
real coverage for a standard normal marginal distribution using block bootstrap
with $l = \lceil 2n^{1/3} \rceil$.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_norm_mu_2}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
    normal distribution with AR coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
    error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:mu2}
\end{figure}

\begin{figure}[bp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_norm_sigma_2}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal standard deviation $\sigma_x$ of an AR(1) process with a
    marginal standard normal distribution with AR 
    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The 
    error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:sigma2}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_norm_phi_2}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
    a marginal standard normal distribution with 
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
    error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:phi2}
\end{figure}

Based on \textbf{Figure~\ref{fig:mu2}}, for negative autocorrelations, the 
coverage 
rates of $\mu$ appear to be lower when
using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
by this change in $l$: for $\phi = -0.4$ and -0.2, they still overcover $\mu$
for smaller values of $n$.

\textbf{Figure~\ref{fig:sigma2}} looks very similar to 
\textbf{Figure~\ref{fig:sigma1}}, but coverage rates of $\sigma$ do look 
slightly lower
especially for negative values of $\phi$, although Student's $t$ CIs are again
not as influenced by this change in $l$. A larger sample size seems necessary
when using other CIs to estimate $\sigma$ for $l = \lceil 2n^{1/3} \rceil$.

As shown in \textbf{Figure~\ref{fig:phi2}},
recentered percentile and standard CIs have slightly lower coverage rates when
estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
Although it is still a problem, the coverage deterioration appears to be less 
dramatic for BCA,
BC, and percentile CIs.

Aside from these differences, the overall changes
in performance when other experimental factors are changed are the same as
when $l = \lceil n^{1/3} \rceil$.

\textbf{Figures~\ref{fig:exp_mu2}--\ref{fig:exp_phi2}} 
summarizes the empirical coverage rates and the 95\% confidence intervals of the 
real coverage for a exponential marginal distribution using block bootstrap
with $l = \lceil 2n^{1/3} \rceil$.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_mu_2}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal mean $\mu$ of a stationary series with marginal unit exponential
    distribution obtained by transforming an AR(1) process with
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_mu2}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_sigma_2}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
    of a stationary series with 
    marginal unit exponential distribution obtained by transforming an AR(1) process
    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
    replicates of
    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_sigma2}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_phi_2}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
    the first-order autocorrelation coefficient of a stationary series
    with marginal unit exponential distribution obtained by transforming an AR(1) 
    process with 
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
    replicates of
    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_phi2}
\end{figure}

For a stationary series with a marginal exponential distribution, altering the 
block size results in the same 
changes in performance of different CIs.

@@

Thank you for the comment. We have now included this comment in the Design 
subsection:

We only
used serial dependences as strong as 0.4, because we only seek to 
establish the 
general trend as the strength of the autocorrelation 
increases, and how it varies depending on the sign of the autocorrelation and 
the parameter of interest.

@@

Thank you for the comment. We have included this discussion of problems 
with block bootstrap in the introduction:

\citet{lahiri1999theoretical} finds that moving block bootstrap has better 
performance than non-overlapping block bootstrap. Additionally, moving block 
bootstrap with nonrandom
block sizes results in lower mean-squared errors than moving block bootstrap
with random block sizes. \citet{buhlmann1999block} notes that a drawback of 
block bootstrap is that it heavily depends on block size, which has to be chosen
by the user of the method.
Even when using the appropriate settings, as noted by
\citet{buhlmann2002bootstraps} observes some general drawbacks of block 
bootstrap --- with respect to how reasonably it imitates the data-generating 
process. In addition, although block bootstrap is primarily used for stationary 
time series, it can be outperformed by other bootstrap schemes for linear time
series and categorical processes. Still, \citet{buhlmann2002bootstraps}
emphasizes that a significant advantage of block bootstrap is its simplicity.
To be more specific, the resampling step of block bootstrap is not 
computationally more difficult than the resampling step of basic bootstrap.
Furthermore, block bootstrap performs better than local bootstrap in terms of
mimicking dependence structures.

\eds{If we include all these drawbacks in the intro, we need to also provide 
some good features of block bootstrap as well, otherwise, why do we care about 
their CI performance?}
\mc{addressed}

We also added this comment in the Discussion section:

We discussed some
drawbacks of block bootstrap in the introduction, which could motivate a similar
simulation study for alternatives to block bootstrap, such 
as AR-Sieve bootstrap, \citep{kreiss1992bootstrap} which 
\citet{buhlmann2002bootstraps} finds to be the best for linear time series.

>>>>

\jy{For each comment, response first and at the end of each response,
  state what was done in the text. I usually don't quote text because
  if you make changes, you need to synchronize at two locations. Learn
  from the first version (which is a real reply letter for a paper).}
\mc{addressed}

@@

Thank you for this suggestion. The motivation behind proposing such an interval 
was based on the 
simulation performance of the BC and BCA intervals, which will be discussed
further in the Results section. This has now been stated in the Recentered
Percentile CI pargarph.

@@

\jy{never use ``below'' because tables/figures are floats.}
\mc{addressed}

Thank you for this idea. We have provided Figure~\ref{fig:mu} as an 
example of what this suggested figure
would look like. 
\jy{1. Reduce the heights; put legend at the bottom; put the
  confidence intervals side by side for each sample size (see this
  paper for example plot:
  \url{https://iopscience.iop.org/article/10.1088/1748-9326/ac14ee/meta}.}
\mc{addressed}

@@

We find that this format
is a little
cluttered to make comparisons, so we have elected to remain with the original 
format.

@@

You are correct. To remedy this, the text highlighting the simulation study with 
an exponential marginal 
distribution from the Appendix has been moved to the Simulation Study 
section.

@@

Thank you for the comment. We expect the CIs that 
are based on bootstrap 
``tables" to depend on the 
asymptotic distribution of the statistics, but we expect such CIs to 
have similar performance for different error structures. For example, under the 
Central
Limit Theorem, we expect the asymptotic distribution of the sample mean to be 
approximately 
normal for both marginal normal distributions and marginal exponential 
distributions. Therefore, we do not expect CIs that are not based on bootstrap
``tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better 
under
non-normal error structures. We have called attention to this in the Exponential
Marginal Distribution subsection of the Design section.

\eds{you will need to add more here.  This concerns the
(asymptotic) distribution of the statistics, not the underlying error 
structure.}
\mc{I changed it a bit... I'm not sure what to say for circumstances in which
“non-parametric” CI 
formulas would work better}

@@

We agree. We have added a comment in the Discussion underlining this CI's
potential for future investigations.

@@

Thank you for pointing this out. We modified the Design section to include a 
specification of the interval type for the coverage rate, as well as an 
acknowledgement of its flaw.

@@

We have also included a figure in the Results section which 
uses exact 
Clopper-Pearson CIs to verify that the choice of interval
for the binomial proportion did not cause undercoverage in this case.

@@

Thank you for the suggestion. However, because of the deterioration for $\phi$, 
we found it hard to fix the limits on 
the 
y-axis without hurting the visualization for the other rows. 
Figure~\ref{fig:alt_phi1} is provided as an 
example:  \eds{refer to the Figure label, and avoid using `below' and `above'
terminology with latex because the figures are not always positioned as we may
have intended.}
\mc{addressed}

@@

Thank you for this comment.
A possible explanation for this is that if a 
stationary series has a positive 
autocorrelation, the effective sample
size is decreased, whereas is a series has a negative autocorrelation, the
effective sample size is increased. Additionally, this seems to have a 
greater effect on the the estimation of the location parameter versus that
of the scale parameter or temporal dependence parameter. We have included a 
similar
comment at the end of the paragraph on estimation of 
$\mu$.

@@

Thank you for pointing this out. The original sentence has been reworded as you
suggested to make it more clear.

@@

Thank you for drawing this to our attention. A citation \citep{calhoun2018} has
now been provided for that comment.

@@

Thank you for the comment. We have now repeated the same simulation study with 
block size as an 
additional experimental factor. The optimal order of block size is 
$\lceil n^{1/3} \rceil$, so we tried the same simulations using 
$l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$. We have included
an Appendix detailing these results.

@@

Thank you for the comment. We only
used serial dependences as strong as 0.4, because we only seek to 
establish the 
general trend as the strength of the autocorrelation 
increases, and how it varies depending on the sign of the autocorrelation and 
the parameter of interest. This justification has been added to the Design 
section.

@@

Thank you for the comment. We have included a discussion of problems 
with block bootstrap in the introduction, while also highlighting its advantages
which motivated this investigation into their CI performance.
